Retrofitting Effect Handlers onto OCaml

### 2020-11-17 retro-concurrency.tex
evaledits

The results are presented in Table~\ref{tab:micro_noperform}. They show that
using effect handlers (concurrency monad) is 13.77$\times$ (67.09$\times$) more
expensive than the idiomatic implementation using non-tail calls. Concurrency
monad suffers due to the heap allocation of continuation frames (which need to
be GCed), where as effect handlers benefit from stack allocation of the frames.
Our concurrency monad, and indeed monadic concurrency libraries such as
Lwt~\cite{lwt} and Async~\cite{async}, also have other downsides; due to the
lack of stack, exceptions, backtraces, and DWARF unwinding are no longer
useful.

>>>>

The results are presented in Table~\ref{tab:micro_noperform}. They show that
using effect handlers (concurrency monad) is 13.77$\times$ (67.09$\times$) more
expensive than the idiomatic implementation using non-tail calls. The concurrency
monad suffers due to the heap allocation of continuation frames (which need to
be GCed), whereas effect handlers benefit from stack allocation of the frames.
Our concurrency monad (and other monadic concurrency libraries such as
Lwt~\cite{lwt} and Async~\cite{async}) also have other downsides -- due to the
lack of a stack, exceptions, backtraces, and DWARF unwinding are no longer
useful.
